\documentclass[11pt]{extarticle}

\usepackage{enumitem}
\usepackage{verbatim}
\usepackage[left=30pt,right=30pt,top=30pt,bottom=50pt]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{tabularx}

\pagenumbering{gobble}
\usepackage[sfdefault]{FiraSans}
\titlespacing*{\section}{0pt}{10pt}{10pt}
\titlespacing*{\subsection}{0pt}{10pt}{0pt}
\titleformat{\section}{\normalfont\large\bfseries}{}{}{}[\titlerule]
\titleformat{\subsection}[runin]{\normalfont\large\bfseries}{}{}{}

\setlist[itemize]{noitemsep}
\setlength{\parskip}{0em}

\newcommand{\resumeHead}[1]{
\section*{#1}
}

\newcommand{\resumeSub}[2]{
\subsection*{#1} \hfill {#2}
}

\begin{document}

\begin{center}
\textbf{\huge{CHARLES GAO}}

charlesgao.c@gmail.com $\bullet$ 514--262--1866 $\bullet$ Waterloo, Canada
\end{center}


\section*{EDUCATION}
\subsection*{University of Waterloo} \hfill {Sept. 2015 --- Apr. 2020}

\textit{Bachelor of Computer Science \& Combinatorics and Optimization }

\section*{EXPERIENCE}
\subsection*{Co-Founder/Full-Stack Developer} \hfill {Sept. 2015 --- Apr. 2020}

\textit{Viafly Technologies, New York}
\begin{itemize}
  \item Created a point-of-sale e-commerce platform with Ruby on Rails, React, and PostgreSQL
  \item Designed a database schema and implemented a PostgreSQL database for a e-commerce website
  \item Designed RESTful API development specifications using Postman API Documentation to plan the development of the website
  \item Added Shopify, Square, Lightspeed third-party authorization (OAuth 2.0)
  \item Automated vendors registration, and products uploading to server database from Shopify, Square, Lightspeed API, and tested using RSpec and mock
  \item Implemented an efficient tag-based product search infrastructure using Algolia
  \item Added online payment process on the back-end using Stripe API
  \item Created the landing webpage and profile pages for shops using React (Redux)
  \item Deployed the platform on Heroku for continuous integration, and set up mail server with AWS
  \item Scraped 50 000\texttt{+} products using Python for front-end testing during early production stage
\end{itemize}

\resumeSub{ETL Developer}{May 2018 --- Mar. 2019}

\textit{Energy Profiles Limited, Toronto}
\begin{itemize}
  \item Built ETL pipelines using Java and Python to efficiently gather, clean and store energy data for analysis
  \item Created data loaders in Java to obtain temperature data from a network of sensors in a buildings
  \item Created a Java scraping framework to increase the development efficiency of utility bills loading tools
  \item Built a Bash toolkit to check the consistency between the data of real and billed consumption
  \item Wrote stored procedures on a Microsoft SQL Server database for report generation
  \item Added unit tests on core functions with JUnit
\end{itemize}

\section*{SKILLS}
\begin{itemize}
  \item \textbf{Languages}: Ruby, JavaScript, Python, C\texttt{++}, Java, Bash
  \item \textbf{Technologies}: Ruby on Rails, Node.js, AWS, Heroku, PostgreSQL, Linux
\end{itemize}

\section*{PROJECTS}
\subsection*{Java Compiler (CS 444) --- C\texttt{++}} \hfill Jan. 2020 --- Apr. 2020

\begin{itemize}
  \item Created a compiler from a subset of Java to x86 Assembly
  \item Implemented a tokenizer and parser from scratch in
    C\texttt{++}
  \item Developed semantics analysis in which includes
    type and hierarchial checking
  \item Integrated a unit testing framework Catch2
    for Test-Driven Development
\end{itemize}

\subsection*{ARM Microkernel (CS 452) --- C} \hfill Sept. 2019 --- Dec. 2019
\begin{itemize}
  \item Created an ARM bare-metal real-time operating system (RTOS)
  \item Implemented context switching, hardware interrupt handler, RS-232 serial port device driver for processes to time-share CPU time
    \end{itemize}

\subsection*{OmnivoxDownloader --- Python} \hfill Sept. 2019 --- Dec. 2019
\begin{itemize}
  \item Built a file downloader with a GUI to synced class documents
    from high school website
  \item Utilized Requests and BeautifulSoup to
    extract tags from school's online learning management website
  \item Built a GUI using wxPython featuring
    a real-time download status frame and a pause/resume option
  \item Synchronized multiple concurrent threads to improve the smoothness
    of the GUI
\end{itemize}

\end{document}
